Supplementary Content for the article *The role of functional diversity in ecosystem regime shifts*

### 2022-04-04 experiments/2_supplement/supplement.Rmd
Some more changes - DOES NOT WORK AT THE MOMENT!

```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=8, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_dots(repl_meth[1,])
```

@@

```{r temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:temp-meth2)', fig.height=8, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=8, fig.width=8, fig.align="center"}
repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
fig_state_vs_o2diff_sidebyside_dots(repl_meth[94,])
```

@@

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=8, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_1e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=8, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_2e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_dots(temp_meth[1,])
```

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=8, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))

@@

fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[13,])

@@

```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=8, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_dots(only_SB_variable[14,])
```

@@

```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_novar1 <- readRDS(here::here("data", "2_supplement", "puzzle1_1.RDS"))
p <- plot_dynamics(sim_res_novar1)
p[[1]] <- p[[1]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[2]] <- p[[2]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[3]] <- p[[3]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[4]] <- p[[4]] + 
  xlab("time(h)") + 
  ylab(expression(log[10](concentration)(µM))) + 
  labs(colour = "substrate")

@@

p <- plot_dynamics(sim_res_highvar1)
p[[1]] <- p[[1]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[2]] <- p[[2]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[3]] <- p[[3]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)(cells~L^{-1})))
p[[4]] <- p[[4]] + 
  xlab("time(h)") + 
  ylab(expression(log[10](concentration)(µM))) + 
  labs(colour = "substrate")

@@

```{r pbdiv-only-1, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-1)', fig.height=8, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_dots(only_PB_variable[sim1,])
```

@@

```{r pbdiv-only-2, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-2)', fig.height=8, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_dots(only_PB_variable[sim2,])
```

>>>>

```{r repl-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth2)', fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(repl_meth[1,])
```

@@

```{r temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:temp-meth2)', fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
```

@@

```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=10, fig.width=8, fig.align="center"}
repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
fig_state_vs_o2diff_sidebyside_alternative(repl_meth[94,])
```

@@

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=10, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_1e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
```

@@

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=10, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_2e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
```

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=10, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))

@@

fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[13,])

@@

```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[14,])
```

@@

```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_novar1 <- readRDS(here::here("data", "2_supplement", "puzzle1_1.RDS"))
p <- plot_dynamics(sim_res_novar1)
p[[1]] <- p[[1]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[2]] <- p[[2]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[3]] <- p[[3]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[4]]$data <- p[[4]]$data %>% 
  dplyr::filter(species != "a") %>%
  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide")
p[[4]] <- p[[4]] + 
  xlab("time (h)") + 
  ylab(expression(log[10](concentration)~(µM))) + 
  labs(colour = "substrate") +
  theme_bw()

@@

p <- plot_dynamics(sim_res_highvar1)
p[[1]] <- p[[1]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[2]] <- p[[2]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[3]] <- p[[3]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[4]]$data <- p[[4]]$data %>% dplyr::filter(species != "a")
p[[4]] <- p[[4]] +
  xlab("time (h)") + 
  ylab(expression(log[10](concentration)~(µM))) + 
  labs(colour = "substrate") +
  theme_bw()

@@

```{r pbdiv-only-1, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-1)', fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim1,])
```

@@

```{r pbdiv-only-2, echo = FALSE,  include=TRUE, fig.cap='(ref:pbdiv-only-2)', fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_PB_variable[sim2,])
```
